Title Goes Here

### 2024-05-31 analysis/paper/paper.qmd
EEO

jobdata_EEO_year_tally <-
  EEO_wordcount %>%
  group_by(year_ad_posted,
           word_count) %>%
  summarise(n = sum(value)) %>%
  mutate(prop = n / sum(n))

fig_ave_length_EEO_per_year <- 
ggplot(jobdata_EEO_year_tally) +
  aes(year_ad_posted) +
  geom_bar() +
  scale_x_discrete(name = "") +
  ylab("Average length of EEO statement by year") +
  theme_minimal(base_size = 28) +
  guides(x = "none")

>>>>

jobdata_EEO_year_tally <-
  EEO_wordcount %>%
  group_by(year_ad_posted) %>%
  summarise(n = mean(word_count))

fig_ave_length_EEO_per_year <- 
ggplot(jobdata_EEO_year_tally) +
  aes(year_ad_posted,n) +
  geom_col() +
  ylab("Average length of EEO statement by year") +
  theme_minimal(base_size = 28) +
  guides(x = "none")

ggplot(EEO_wordcount) +
  aes(year_ad_posted, word_count) +
  geom_boxplot() +
  geom_quasirandom()
